---
title: "Analysis Script RSAcover"
author: "TBD"
date: "2025-02-10"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---
Supress messages in this document so that the output is cleaner.
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
Import packages.
```{r}
rm(list = ls())
options(warn = -1)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggplot2)
library(aida)
library(BayesFactor)
library(pwr)
library(brms)
library(emmeans)
library(effsize)
library(HDInterval)
```

Set up theme for ggplot.

```{r}
theme_set(theme_aida())

##################################################
## CSP-colors
##################################################
CSP_colors = c(
  "#7581B3", "#99C2C2", "#C65353", "#E2BA78", "#5C7457", "#575463",
  "#B0B7D4", "#66A3A3", "#DB9494", "#D49735", "#9BB096", "#D4D3D9",
  "#414C76", "#993333"
  )
# setting theme colors globally
scale_colour_discrete <- function(...) {
  scale_colour_manual(..., values = CSP_colors)
}
scale_fill_discrete <- function(...) {
  scale_fill_manual(..., values = CSP_colors)
}
```

# Data Import & Preprocessing

## Import data batch1

```{r}
data <- read.csv("../../data/pilot-1-n20/results.csv")
```

Factorise variables: id, informationSource
```{r}
#data$id <- as.factor(1:nrow(data))
data$F1_NPforms <- as.factor(data$F1_NPforms)
data$F2_matchness <- as.factor(data$F2_matchness)
```

Drop unnecessary columns and NA values. Filter out practice and filler items.
```{r}
practice_itemNr_list <- c(801,802,803)
filler_itemNr_list <- c(901,902,903,904,905,906)
grouped_itemNr_list <- c(73:144)

data_filler <- data %>% select(submission_id,, 
                               acceptability, 
                               List, itemNr, 
                               F1_NPforms, 
                               F2_matchness)%>%
  filter(itemNr %in% filler_itemNr_list)

data <- data %>% select(submission_id, 
                        acceptability, 
                        List, 
                        itemNr, 
                        F1_NPforms, 
                        F2_matchness) %>% 
  filter(!itemNr %in% practice_itemNr_list & !itemNr %in% filler_itemNr_list)

data_without_grouped <- data %>% filter(!itemNr %in% grouped_itemNr_list)

```

Show list distribution.
```{r}
data %>% group_by(List) %>% summarise(n = n()/24)
```


# Exploratory Data Analysis

## Histogram of Updated Probabilities

```{r}
ggplot(data, aes(x = acceptability)) +
  geom_histogram(binwidth = 5, fill = CSP_colors[1]) +
  facet_wrap(F1_NPforms ~ F2_matchness, scales = "free_y") +
  labs(title = "Distribution of Acceptability Ratings",
       x = "Acceptability",
       y = "Frequency")

```

## Density plot of Updated Probabilities

```{r}
ggplot(data, aes(x = acceptability)) +
  geom_density(fill = CSP_colors[1]) +
  facet_wrap(F1_NPforms ~ F2_matchness, scales = "free_y") +
  labs(title = "Distribution of updated probs",
       x = "Acceptability",
       y = "Density")

```

## Boxplot of Probabilities by Information Source and Decision Type

```{r}

p1 <- ggplot(data_without_grouped, aes(x = F1_NPforms, y = acceptability, fill = F2_matchness)) +
  geom_boxplot() +
  labs(title = "Acceptability Ratings by F1 and F2",
       x = "NP Structures",
       y = "Acceptability")

ggsave("fig1.png", p1, width = 6, height = 4, dpi = 300)

p1
```

## Table of updated probabilities by information source: mean, sd, and N.
```{r}
data %>%
  group_by(F1_NPforms, F2_matchness) %>%
  summarise(
    Mean = mean(acceptability, na.rm = TRUE),
    SD = sd(acceptability, na.rm = TRUE),
    N = n()
  )
```
## Show how many false controls are answered correctly.
```{r}
false_control_itemNr_list <- c(902,904,906)
data_filler %>% group_by(itemNr) %>% summarise(mean(acceptability))

# Make a plot with mean and CIs for better visualization
ggplot(data_filler, aes(x = itemNr, y = acceptability)) +
  stat_summary(fun.data = mean_cl_normal) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  labs(
    title = "Acceptability Ratings for False Controls \n (902, 904, 906)",
    x = "Item Number",
    y = "Acceptability"
  )
```



# Inferential Statistics

Normality test. (Passed!)
```{r}
# all data
shapiro.test(data$acceptability)
# only datqa from the 'direct-source' condition
#shapiro.test(data |> filter(informationSource == "direct") |> pull(update))
# only datqa from the 'indirect-source' condition
#shapiro.test(data |> filter(informationSource == "indirect") |> pull(update))
```
## Regression with LMER
```{r}
lmer_model_full <- lmer(acceptability ~ F1_NPforms * F2_matchness + (1|submission_id) + (1|itemNr), data = data)
lmer_model_reduced <- lmer(acceptability ~ F1_NPforms + F2_matchness + (1|submission_id) + (1|itemNr), data = data)
anova(lmer_model_reduced, lmer_model_full)
```
```{r}
summary(lmer_model_full)
```

Post-hoc tests
```{r}
emmeans(lmer_model_full, pairwise ~ F1_NPforms * F2_matchness, adjust = "bonferroni")
```


## Bayesian regression model:
```{r}
brm_full_model <- brm(acceptability ~ F1_NPforms * F2_matchness + (1|submission_id) + (1|itemNr), data = data, sample_prior = "yes", prior = c(brms::prior("normal(0, 100)")))

summary(brm_full_model)
# posterior predictive checks
brms::pp_check(brm_full_model, ndraws = 50)
```

