---
title: "Analysis Script RSAcover"
author: "TBD"
date: "2025-02-10"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---
Supress messages in this document so that the output is cleaner.
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
Import packages.
```{r}
rm(list = ls())
options(warn = -1)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggplot2)
library(aida)
library(BayesFactor)
library(pwr)
library(brms)
library(emmeans)
library(effsize)
library(HDInterval)
```

Set up theme for ggplot.

```{r}
theme_set(theme_aida())

##################################################
## CSP-colors
##################################################
CSP_colors = c(
  "#7581B3", "#99C2C2", "#C65353", "#E2BA78", "#5C7457", "#575463",
  "#B0B7D4", "#66A3A3", "#DB9494", "#D49735", "#9BB096", "#D4D3D9",
  "#414C76", "#993333"
  )
# setting theme colors globally
scale_colour_discrete <- function(...) {
  scale_colour_manual(..., values = CSP_colors)
}
scale_fill_discrete <- function(...) {
  scale_fill_manual(..., values = CSP_colors)
}
```

# Data Import & Preprocessing

## Import data batch1

```{r}
data <- read.csv("../../data/pilot-2b/results.csv")
```

Factorise variables: id, informationSource
```{r}
#data$id <- as.factor(1:nrow(data))
data$F1_NP <- as.factor(data$F1_NP)
data$F2_visual <- as.factor(data$F2_visual)

data %>% mutate(alternative = ifelse(itemNr < 73, "yes", "no") ) -> data

```

Drop unnecessary columns and NA values. Filter out practice and filler items.
```{r}
practice_itemNr_list <- c(801,802,803)
filler_itemNr_list <- c(901:924)

data_filler <- data %>% select(submission_id,, 
                               acceptability, 
                               List, itemNr,
                               F1_NP, 
                               F2_visual)%>%
  filter(itemNr %in% filler_itemNr_list)

data <- data %>% select(submission_id, 
                        acceptability, 
                        List, 
                        itemNr,
                        alternative,
                        F1_NP, 
                        F2_visual) %>% 
  filter(!itemNr %in% practice_itemNr_list & !itemNr %in% filler_itemNr_list)


```

Show list distribution.
```{r}
data %>% group_by(List) %>% summarise(n = n()/24)
```


# Exploratory Data Analysis

## Histogram of Updated Probabilities

```{r}
ggplot(data, aes(x = acceptability)) +
  geom_histogram(binwidth = 5, fill = CSP_colors[1]) +
  facet_wrap(alternative ~ F2_visual, scales = "free_y") +
  labs(title = "Distribution of Acceptability Ratings",
       x = "Acceptability",
       y = "Frequency")

```

## Density plot of Updated Probabilities

```{r}
ggplot(data, aes(x = acceptability)) +
  geom_density(fill = CSP_colors[1]) +
  facet_wrap(~ F2_visual, scales = "free_y") +
  labs(title = "Distribution of updated probs",
       x = "Acceptability",
       y = "Density")

```

## Boxplot of Probabilities by Information Source and Decision Type

```{r}
library(ggpubr)

# Ensure factor order
data$F2_visual <- factor(data$F2_visual,
                         levels = c("notGrouped", "randomGrouped", "colorGrouped"))

data$condition <- paste(data$alternative, data$F2_visual, sep = "_")

data$condition <- factor(data$condition,
                         levels = c("no_notGrouped", "no_randomGrouped", "no_colorGrouped",
                                    "yes_notGrouped", "yes_randomGrouped", "yes_colorGrouped"))

sig_df <- data.frame(
  group1 = c(
    "no_randomGrouped",  # within 'no'
    "no_notGrouped",     # across
    "no_randomGrouped",  # across
    "no_colorGrouped",   # across
    "yes_randomGrouped"  # within 'yes'
  ),
  group2 = c(
    "no_colorGrouped",        # within 'no'
    "yes_notGrouped",         # across
    "yes_randomGrouped",      # across
    "yes_colorGrouped",       # across
    "yes_colorGrouped"        # within 'yes'
  ),
  y.position = c(115, 120, 125, 130, 135),
  significance = c("***", "***", "***", "***", "***")
)

# Create plot
p1 <- ggplot(data, aes(x = condition, y = acceptability)) +
  geom_boxplot(aes(fill = F2_visual)) +
  stat_pvalue_manual(sig_df, label = "significance", tip.length = 0.01) +
  #facet_wrap(~alternative) +  # 👈 facet by "alternative"
  labs(
    x = "Visual Context",
    y = "Acceptability"
  ) +
  theme(
  axis.text.x = element_text(angle = 30, hjust = 1)
) + theme(legend.position = "bottom")

# Save to file
ggsave("fig1.png", p1, width = 7, height = 5, dpi = 300)

# Show plot
p1
```

## Table of updated probabilities by information source: mean, sd, and N.
```{r}
data %>%
  group_by(F2_visual) %>%
  summarise(
    Mean = mean(acceptability, na.rm = TRUE),
    SD = sd(acceptability, na.rm = TRUE),
    N = n()
  )
```
## Show how many false controls are answered correctly.
```{r}
false_control_itemNr_list <- seq(901, 924, 2)
data_filler %>% group_by(itemNr) %>% summarise(mean(acceptability))

# Make a plot with mean and CIs for better visualization
data_filler %>% filter(itemNr %in% false_control_itemNr_list) %>% ggplot(aes(x = F1_NP, y = acceptability)) +
  stat_summary(fun.data = mean_cl_normal) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  labs(
    title = "Acceptability Ratings for False Controls \n (902, 904, 906)",
    x = "Item Number",
    y = "Acceptability"
  )
```



# Inferential Statistics

Normality test. (Passed!)
```{r}
# all data
shapiro.test(data$acceptability) #Not passed.
```
## Regression with LMER
```{r}
data$F1_NP <- droplevels(data$F1_NP)
lmer_model_full <- lmer(acceptability ~ F2_visual * alternative + (1|submission_id) + (1|itemNr), data = data)
lmer_model_reduced <- lmer(acceptability ~ F2_visual + alternative + (1|submission_id) + (1|itemNr), data = data)
anova(lmer_model_reduced, lmer_model_full)
```
```{r}
summary(lmer_model_full)
```

Post-hoc tests
```{r}
emmeans(lmer_model_full, pairwise ~ alternative * F2_visual, adjust = "bonferroni")
```


## Bayesian regression model:
```{r}
brm_full_model <- brm(acceptability ~ F1_NPforms * F2_matchness + (1|submission_id) + (1|itemNr), data = data, sample_prior = "yes", prior = c(brms::prior("normal(0, 100)")), save_pars = save_pars(all = TRUE))

bayestestR::describe_posterior(brm_full_model,
                               centrality = "mean",
                                test = c("p_direction", "p_significance"),
)
# posterior predictive checks
brms::pp_check(brm_full_model, ndraws = 50)
```
Fit a modell without interaction and compute the Bayes factor.
```{r}
brm_reduced_model <- brm(acceptability ~ F1_NPforms + F2_matchness + (1|submission_id) + (1|itemNr), data = data, sample_prior = "yes", prior = c(brms::prior("normal(0, 100)")), save_pars = save_pars(all = TRUE))

```
```{r}
bayes_factor(brm_reduced_model, brm_full_model, silent = TRUE)
```
```{r}
pairs(emmeans(brm_full_model, ~ F1_NPforms * F2_matchness), adjust = "bonferroni")
```


